---
title: "Checkpoint 1: EDA"
format: revealjs
editor: visual
---

## Does healthcare access affect the number of preventable hospital stays of certain racial groups at the county level?

- Reduce preventable hospitalizations
- Equitable resource allocation
- Focus efforts where help is needed most

------------------------------------------------------------------------

## Data

**Source:**<br>
2025 County Health Rankings Analytic Dataset


**Variables of Interest:**\
enter here

**Preprocessing Highlights:**\
enter here

------------------------------------------------------------------------

## EDA Plot 1: PCP Ratio vs Preventable Stays

```{r}
#source("payson_file.R")
#print(map_inter)
```

------------------------------------------------------------------------

## EDA Plot 2: Uninsured Rate vs Preventable Stays

```{r}
# plot here 
```

------------------------------------------------------------------------

## Methods (Planned)

**Modeling Strategy:**\
- Use ....

**Justification:**\
- give reasons

------------------------------------------------------------------------

## Plan of Action

\*\* Completed:\*\*\
- Defined research question - Cleaned and preprocessed data - Created two EDA visualizations

\*\* Next Steps:\*\*\
- Build linear regression models with interaction terms\
- Interpret race-specific associations\
- Check model assumptions and fit\
- Create tables/figures for final presentation\
- Draft and revise final poster
