---
title: "Checkpoint 1 Presentation"
format: revealjs
editor: visual
---

## Preventable Hospital stays vary with healthcare access across racial groups

**Research Question:**\
Does healthcare access affect the number of preventable hospital stays for different racial groups at the county level?

## **Why It Matters:** 

------------------------------------------------------------------------

## Data

**Source:**\
- 2025 County Health Rankings Analytic Dataset

**Variables of Interest:**\
- Preventable Hospital Stays, Primary Care Physician Ratio, Uninsured Rate - others things - County-level racial groupings (White Majority vs White Minority)

**Preprocessing Highlights:**\
- explain how we did white majority vs minority

------------------------------------------------------------------------

## EDA Plot 1: PCP Ratio vs Preventable Stays

```{r}
# plot here  
```

------------------------------------------------------------------------

## EDA Plot 2: Uninsured Rate vs Preventable Stays

```{r}
# plot here 
```

------------------------------------------------------------------------

## Methods (Planned)

**Modeling Strategy:**\
- Use ....

**Justification:**\
- give reasons

------------------------------------------------------------------------

## Plan of Action

\*\* Completed:\*\*\
- Defined research question - Cleaned and preprocessed data - Created two EDA visualizations

\*\* Next Steps:\*\*\
- Build linear regression models with interaction terms\
- Interpret race-specific associations\
- Check model assumptions and fit\
- Create tables/figures for final presentation\
- Draft and revise final poster
