---
title: "Checkpoint 1 Presentation"
format: revealjs
editor: visual
---

## Introduction


**Project Question:**\
\> Does healthcare access (e.g., primary care physicians, uninsured rate) affect the number of preventable hospital stays for different racial groups at the county level?

**Why It Matters:**\
- say things here

------------------------------------------------------------------------

## Data

**Source:**\
- 2025 County Health Rankings Analytic Dataset

**Variables of Interest:**\
- Preventable Hospital Stays - Primary Care Physician Ratio - Uninsured Rate - others things 
- County-level racial groupings (White Majority vs White Minority)

**Preprocessing Highlights:**\
- explain how we did white majority vs minority 

------------------------------------------------------------------------

## EDA Plot 1: PCP Ratio vs Preventable Stays

```{r}
# plot here 
```

------------------------------------------------------------------------

## EDA Plot 2: Uninsured Rate vs Preventable Stays

```{r}
# plot here 
```

------------------------------------------------------------------------

## Methods (Planned)

**Modeling Strategy:**\
- Use ....

**Justification:**\
- give reasons 

------------------------------------------------------------------------

## Plan of Action

\*\* Completed:\*\*\
- Defined research question
- Cleaned and preprocessed data
- Created two EDA visualizations

\*\* Next Steps:\*\*\
- Build linear regression models with interaction terms\
- Interpret race-specific associations\
- Check model assumptions and fit\
- Create tables/figures for final presentation\
- Draft and revise final poster
